A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 4_method.tex
describe beading schemes section not as generalization section

This section explains how we generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.

>>>>

This section explains how we generate toolpaths using our framework with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
In \cref{sec_generalization} we describe how to apply the framework to different beading schemes and we show several such beading schemes.

### 2019-08-28 5_generalization.tex
describe beading schemes section not as generalization section

\section{Generalization}\label{sec_generalization}
A critical component in toolpath generation is how to distribute the beads over the feature radius.
While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3d printer or material.

% In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
% The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
% Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
% In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
% There are several schemes one can take for determining the distribution of bead widths.
% We will formalize several schemes and describe the set of parameters these schemes require.

>>>>

\section{Beading schemes}\label{sec_generalization}
A critical component in toolpath generation is how to distribute the beads over the feature radius.
While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3d printer or material.
